
%------------------------
% Resume Template
% Author : Anubhav Singh
% Github : https://github.com/xprilion
% License : MIT
%------------------------

\documentclass[a4paper,20pt]{article}

\usepackage[inline]{enumitem}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.530in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-0.7in}
\addtolength{\textheight}{1.11in}

\urlstyle{rm}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemWithoutTitle}[1]{
  \item\small{
    {\vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{#3} & \textit{#4} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-3pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-----------------------------
%%%%%%  CV STARTS HERE  %%%%%%

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\LARGE Daniel Alonso}} & Email: {\color{blue}\href{mailto:}{d@dac.sg}}\\
  Website: {\color{blue}\href{https://dac.sg}{dac.sg}} & Github: ~~~{\color{blue}\href{https://github.com/dreth}{@dreth}}
\end{tabular*}

%----------SECTIONS TO ITERATE ON-----------------



            
%-----------INTRODUCTION-----------------
\vspace{-3pt}
\section{Introduction}
{\begin{itemize} \itemsep-0.24em
\item {I'm a developer, former data scientist and teacher. I have had a very diverse set of tasks and challenges during my career but I'm always open to new challenges and ideas. Though I'm especially interested in making impact. Saving my team time and money, automating manual tasks, setting up simple infrastructure to satisfy business needs at the lowest possible cost. I like to untangle technological chaos and streamlining software/data management. I love making internal productivity leaps for the business through technology.}
\end{itemize}}
        


            
%-----------SKILLS-----------------
\vspace{-3pt}
\section{Skills Summary}
  \resumeSubHeadingListStart
            
        
\vspace{-1pt}
\resumeSubItem{Languages}{~~~~~Python, SQL, Shell scripting, JavaScript, Go, R, Solidity, LaTeX, HTML, CSS, Julia, MATLAB, VBA.}
\vspace{-1pt}
\resumeSubItem{Data}{~~~~~~~~Data Manip./analysis/viz/ML. Metabase. DB design, PostgreSQL, MySQL, MSSQL, ClickHouse.}
\vspace{-1pt}
\resumeSubItem{Tools}{~~~~~~~~~~~Git, GH actions, docker/compose, Kubernetes, CI/CD, networking, linux servers cloud/on-premise.\\~~~~~~~~~~~~~~~~~~~~~~~~HTMX, TailwindCSS, Django, DRF, FastAPI, Fiber-go, Gin, React, ORMs. RShiny, Rmd, Dash.\\~~~~~~~~~~~~~~~~~~~~~~~~Unix shells (zsh, bash, sh, etc.) y CLIs, SRE. Jira, Confluence. Spreadsheets/MS Office.}
\vspace{-1pt}
\resumeSubItem{Other}{~~~~~~~~~~~~~Documentation, GH Issues, Blockchain/DeFi, Agile/Scrum, Code reviews, OpenAI API, GIMP.\\~~~~~~~~~~~~~~~~~~~~~~~~Passion for languages, development, teaching, writing, quality, and presenting information.}
\resumeSubHeadingListEnd


            
%-----------LANGUAGES-----------------
\vspace{-15pt}
\section{Languages}
  \begin{center}
  \begin{itemize*}
        
  \item \textbf{Native:} Spanish, English.
  \item \textbf{Basic:} Malay, Dutch, Italian.
\end{itemize*}
\end{center}


            
%-----------EDUCATION-----------------
\vspace{-15pt}
\section{Education}
\resumeSubHeadingListStart
        
  \resumeSubheading
    {Universidad Carlos III de Madrid}{Madrid, Spain}
    {Master in Statistics for Data Science}{September 2020 - September 2021}
\begin{itemize} \itemsep-0.24em
  \item Working with R/Python/Julia for statistical analysis, data viz. and reports and collaborative projects
  \item Building statistical models, ML models, and interactive web applications with RShiny and Dash
\end{itemize}
\vspace{-2pt}
  \resumeSubheading
    {Instituto Tecnológico de Santo Domingo}{Santo Domingo, Dominican Republic}
    {Bachelor's degree in Mathematics and Actuarial Science}{August 2015 - October 2019}
\begin{itemize} \itemsep-0.24em
  \item Studied calculus, functional analysis, actuarial mathematics, financial mathematics, statistics
  \item Perform financial data modelling and predictions as well as learn to code
\end{itemize}
\resumeSubHeadingListEnd


            
%-----------WORK-----------------
\vspace{-12pt}
\section{Work experience}
  \resumeSubHeadingListStart
        
  \resumeSubheading{Neolux Energy}{Madrid, Spain (remote)}
    {Tech Lead (Full-time)}{January 2023 - Present}
\begin{itemize} \itemsep-0.24em
  \item Turning existing software useful. Saved 1-2k € monthly on infra/service costs self-hosting software.
  \item Cont. monitoring and management, hosting and deployment of on-premise apps (w/ docker, traefik, Cloudflare)
  \item Python backend development using Django, DRF, FastAPI (REST APIs, GraphQL, ORMs)
  \item Building and maintaining interactive webapps with streamlit and frontend dev. with react
  \item Managing AWS infra (EKS, EC2, S3, ...), developing CI/CD using GH actions
  \item Jira project management, documentation using confluence, software design decisionmaking
  \item Collaborating with our CTO to manage the tech team, code reviews and deployments
\end{itemize}
\vspace{-2pt}
  \resumeSubheading{Study break}{Madrid, Spain}
    {Career break to study and write (Full-time)}{February 2022 - December 2022}
\begin{itemize} \itemsep-0.24em
  \item Setting up two servers, learning about server infra, containers (docker, kubernetes) and networking
  \item Running an Ethereum node and several docker stacks for personal use (Nextcloud, VPN, etc..)
  \item Solving smart contract auditing CTFs like Ethernaut, Capture the Ether and Damn Vulnerable DeFi
  \item Learning solidity and delving into smart contract security, multisig wallets, the EVM and more
  \item Writing at length about topics like data privacy, cryptocurrency investments, my home server setup, etc..
  \item Pivoting to software development, system administration, networking, linux servers, cloud and consulting
  \item Coding small CLI tools, telegram bots and other utilities and posting them on my github
  \item Further developing my personal website and started to write a book
\end{itemize}
\vspace{-2pt}
  \resumeSubheading{Populate}{Madrid, Spain (remote)}
    {Python developer \& Data scientist (Full-time)}{September 2021 - February 2022}
\begin{itemize} \itemsep-0.24em
  \item Developing a data integrity checking pipeline using Python and Great Expectations
  \item Build interactive dashboards using Metabase, SQL queries and Metabase's native UI
  \item Data analysis using pandas, numpy, matplotlib, metabase, seaborn, R and streamlit
  \item Improving the accuracy (c. 10 pct.) of a TensorFlow deep learning model and some smaller scikit-learn models
  \item Quit due to burnout and change of interests to write, study and pursue new knowledge for a while
\end{itemize}
\vspace{-2pt}
  \resumeSubheading{Cervecería Nacional Dominicana}{Santo Domingo, Dominican Republic (remote)}
    {Data scientist (Full-time)}{March 2020 - August 2020}
\begin{itemize} \itemsep-0.24em
  \item Cleaning up and manipulating data with pandas for analysis. Building ML models.
  \item Clustering clients based on their product sales to target market niches
  \item Utilizing Azure Databricks and PySpark to deploy, clean up and tune models for sales prediction
  \item Quit the company to move to Spain to do my master's degree
\end{itemize}
\vspace{-2pt}
  \resumeSubheading{Referencia Laboratorio Clínico S.A.}{Santo Domingo, Dominican Republic}
    {Python developer \& Lead data scientist (Full-time)}{August 2019 - March 2020}
\begin{itemize} \itemsep-0.24em
  \item Developed automation scripts which allowed to 15-20x the output of genetic family relations tests.
  \item Extracting, cleaning up, processing, visualizing and manipulating data with pandas, numpy, matplotlib, seaborn
  \item Constructing DBs from raw text data using python and a strong use of RegEx. Analyzing genetic sequence data
  \item Quit because I felt I had made the impact I wanted to make in the company and wanted new challenges
\end{itemize}
\vspace{-2pt}
  \resumeSubheading{Seguros Sura}{Santo Domingo, Dominican Republic}
    {Vehicle insurance subscription analyst (Full-time)}{April 2019 - August 2019}
\begin{itemize} \itemsep-0.24em
  \item Building spreadsheets with macros (VBA) improving the quote-giving process boosting team productivity with the tool, which had some broken features that I also decided to fix.
  \item Pricing/discount analysis and quoting individual vehicle insurance policies and fleets of vehicles
  \item Quit to pursue new challenges as I felt I made the impact I wanted to make. The tool is still used daily.
\end{itemize}
\vspace{-2pt}
  \resumeSubheading{Sainz Tutoring}{Santo Domingo, Dominican Republic}
    {Mathematics, programming \& physics tutor (Part-time)}{November 2016 - May 2019}
\begin{itemize} \itemsep-0.24em
  \item Math, programming and physics tutor for high school and university students
\end{itemize}
\vspace{-2pt}
  \resumeSubheading{Business Computer POS}{Santo Domingo, Dominican Republic}
    {IT Technician (Full-time)}{May 2015 - October 2015}
\begin{itemize} \itemsep-0.24em
  \item Repairing and maintaining computers and peripherals / Installing and configuring software
\end{itemize}
\vspace{-2pt}
  \resumeSubheading{Alonso \& Colado SRL}{Santo Domingo, Dominican Republic}
    {Marketing manager (Full-time)}{January 2014 - August 2014}
\begin{itemize} \itemsep-0.24em
  \item Designing ads and general image editing / Data entry, mass emailing to customers and CM
\end{itemize}
\resumeSubHeadingListEnd


            
%-----------PROJECTSANDBLOG-----------------
\vspace{-9pt}
\section{Blog \& Certifications}
\textbf{View all my \href{https://dac.sg/blog}{articles}, and \href{https://www.linkedin.com/in/dreth/details/certifications/}{certifications}.}
        

\end{document}
